Nested Stochastic Block Models Applied to the Analysis of Single Cell Data

### 2021-04-15 manuscript.tex
Added Visium data

\subsection*{Model hierarchy contains biological information}

>>>>

\subsection*{Hierarchy modelling is accurate in defining biological properties}

When grouping is performed by optimization of modularity, there is often the implicit assumption that the resolution parameter reflects a hierarchical structure of the graph, that is communities are consistently grouped at lower resolutions. Not only this assumption is wrong, but it may also lead to spurious groupings in real experiments, whereas nSBM inherently encodes hierarchies by merging communities in a tree. To show this effect we took advantage of public spatial RNA dataset of murine cerebellum profiled with 10X Visium HD technology [\textcolor{red}{REF}], as provided by the recently introduced package SquidPy \cite{Palla_Theis_2021}, for which we chose to stick to the given tissue annotation by the package authors. At default resolution, modularity optimization resolves the tissue structure, as does the first level of the nSBM hierarchy (Fig. \ref{Figure_Visium}). When resolution is decreased (\emph{e.g.} $\gamma = 0.5$), the dentate gyrus is incorrectly merged to the hippocampus, whereas nSBM correctly identifies the pyramidal layer.

\begin{figure}[H]
\centering
\includegraphics[keepaspectratio,width=\textwidth,height=0.55\textheight]{Figure_Visium_Spatial.png}
\caption[]{Analysis of spatial transcriptomics of cerebellum by Visium HD. In the first panel, original tissue annotation is given. Tissues are well defined at default resolution for the standard approach. When resolution is decreased to $\gamma = 0.5$, cells from the dentate gyrus are merged to the hippocampus. When nSBM is used, the structure of the pyramidal is maintained at different levels of the hierarchy}\label{Figure_Visium}
\end{figure}
